Multimodal Contrastive Learning for Physical Object Retrieval

### 2022-01-26 Paper/lit-search.tex
Paper update before SIGIR writeup

>>>>

\subsection{Multimodal Contrastive Training for Visual Representation Learning}
\href{https://arxiv.org/pdf/2104.12836.pdf}{paper pdf}

\subsection{CrossCLR: Cross-modal Contrastive Learning For Multi-modal Video Representations}
\href{https://openaccess.thecvf.com/content/ICCV2021/papers/Zolfaghari_CrossCLR_Cross-Modal_Contrastive_Learning_for_Multi-Modal_Video_Representations_ICCV_2021_paper.pdf}{paper pdf}
